\documentclass{constitution}
\usepackage{pifont}
\definecolor{Gold}{rgb}{0.83, 0.69, 0.22}

\title{OpenUTD}
\author{Calvin Ross \and Logan Moon \and Alejandro Arredondo \and Nathan Snead \and Michael Murphey}
\date{\today. Version 1}

\begin{document}

\maketitle
\begin{center}
  OpenUTD is a student organization dedicated to the teaching and advocacy of Linux, open source, and free software of all kinds.
\end{center}

\section{Essentials}

\subsection{Member Qualification Clause}

Membership of OpenUTD is available to all students currently attending the
University of Texas at Dallas. Membership is available to undergraduate and
graduate students alike and is not restrictive based on student major or field
of study.

\subsection{Non-Discriminative Clause}

Membership may not be used as a means for discrimination toward the students of
the University of Texas at Dallas based on a student's age, sex, ethnicity,
religion, disability, or sexual preference. Further categories of discrimination
may be defined at the discretion of the prospective members.

\section{Managerial}

\subsection{Officer Qualification Clause}

Undergraduate members of OpenUTD are qualified to be appointed officer positions
within the organization at the discretion of the sitting officers.

\subsection{Officer Authority Clause}

Internal operations regard the interactions defined by the officers that pertain
directly to students who are either members of OpenUTD or are attendents to an
OpenUTD hosted event. The officers of OpenUTD share equal authority over the
internal operation of the organization. External operations regard interactions
of the organization with resources provided by other organizations, the
University, or the Student Organization Center. Authority over external
operations are divided among the officers in compliance with the Student
Organization Center's guidelines.

The position of President is appointed among the sitting officers of the
organization. The President is responsible for representing the organization in
situations that require it as well as appointing another officer as Vice
President. The position of Vice President designates the successor of the
President.

The Treasurer is appointed to manage organization expenses and handle banking.
The Treasurer, along with the President and Vice President, are given permission
to use organization funds in the service of OpenUTD's resources and events.

\subsection{Officer Succession Clause}

If the number of sitting officers for OpenUTD falls below the number required by
the Student Organization Center, the remaining sitting officers of the
organization will choose members to be promoted to officer positions.

\subsection{Officer Meeting Clause}

In ideal circumstances, the officers of OpenUTD are to meet once every two weeks
at a minimum.

\section{Principals}

\subsection{Open Source Software Advocacy}

OpenUTD defines Open Source software as software for which: 

\begin{enumerate}
\item Users are allowed the freedom to use open source software for any purpose.
\item Users are allowed access to the source code of open source software.
\item Users are free to create derivative works based on the source code of open
  source software.
\item Users are free to distribute software either as a copy of open source
  software or as a derivative work of open source software.
\item Users are free to combine open source software with other software.
\end{enumerate}

\noindent
All events and resources hosted by OpenUTD should be in the service of
advocating or teaching material relating to free software as defined by the Free
Software Foundation or to open source software as defined above.

\subsection{Axiom of Choice \color{Gold}\ding{72}}

Neither members nor officers of OpenUTD may persecute or discriminate other
students (whether they be members of the organization or otherwise) based on
their choice of software. There are no software requirements to become a member
of OpenUTD, and members should never be pressured to switch to Linux or to use
any particular software in order to properly engage with the organization.

\subsection{Education Initiative}

OpenUTD is responsible for providing resources to the students of the University
of Texas at Dallas for teach the usage of free and open source software.

\subsection{Community Initiative}

OpenUTD is responsible for providing mediums by which students at the University
of Texas at Dallas may communicate and share their interests in free and open
source software.

\subsection{Semester Project}

OpenUTD is responsible for establishing and organizing an open sourced project
each semester. It is not required to complete a project within the semester,
however, it is required for one to be established. A project is allowed to be
dedicated to the maintaining or the continuation of an existing project.

\end{document}
